I would like to thank everyone who have helped me.

Especially thanks to my advisor Patrick Skubic, SS/3L + jets analysis convenor Ximo Poveda Torres, and post doctor Judita Mamu\v{z}i\'{c}.
%
Patrick gave me enough freedom and space to work on the project related to the analysis I was interesting in.
He helped me to handle all the things related to the university when I based at CERN for the past three years.
He also guided me, discussed with me on every Tuesday and Thursday, gave me a lot of useful feedback, and provided me the financial support for my entire Ph.D. life.
%
Ximo is a very good mentor and friend while I was at CERN.
When I got stuck in some technical parts in doing the analysis, Ximo always used his abundant experiences and knowledge to help me to solve the problem.
Not only helping me in the research, Ximo also helped me to accommodate myself to the new life at CERN.
Without Ximo's great help, I couldn't finish my dissertation smoothly and successfully.
%
Judita kindly agreed to help me working on the NUHM2 interpretation in the Higgsino LSP research after I finished the study on the SS/3L + jets analysis.
She used the experiences about the NUHM2 study, which she accumulated in Run 1 $\sqrt{s} = 8$~{\TeV}, providing me many instructions about doing the NUHM2 analysis and writing the note and my dissertation.
Especially, she spent a lot of time to prepare the NUHM2 compressed + compressed MC sample productions, to develop the script using HiggsinoFitter, to answer various questions from the editorial board.
With her supports, I can finish the NUHM2 study in a very short period.
%

Thanks to all my friends at CERN and OU for the good times we enjoyed together in exploring delicious food, traveling, hiking, bouldering, skiing, and boxing.
Thanks to my ex-girlfriend to warm my heart, to encourage me, and to love me, making me felt happiness in the first half of my Ph.D. life.
Thanks to my brother taking care of my parents when I am far away from Taiwan.
Finally, many thanks to my parents for everything they bestowed on me.

%I would like to deeply thank all of my teachers and professors over the 20 years of my academic journey, for instilling in me a deep, unquenchable desire to learn. 
%\begin{quotation}
%\raggedright{\emph{``If you don't know, the thing to do is not to get scared, but to learn.''}} \\
%\raggedleft{- Ayn Rand, Atlas Shrugged}
%\end{quotation}

%I would also like to thank all of my family and friends who have helped motivate and encourage me in my pursuit of this degree. 
%\begin{quotation}
%\raggedright{\emph{``It's the job that's never started as takes longest to finish.''}} \\
%\raggedleft{- J.R.R. Tolkien, The Lord of the Rings}
%\end{quotation}

%Lastly, I would like to thank my wife for not only supporting me through the entire process, but actually pushing me to be the best me I could be. Thank you for living this adventure with me!
%\begin{quotation}
%\raggedright{\emph{``I am a wife-made man.''}} \\
%\raggedleft{- Danny Kaye} 
%\end{quotation}
%\begin{quotation}
%\raggedright{\emph{``I knew when I met you an adventure was going to happen.''}} \\
%\raggedleft{- A.A. Milne, Winnie the Pooh} 
%\end{quotation}

